Continuous Generalization of Buildings \protect\\ by Growing and Merging

### 2017-08-25 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
working on simplify grown buildings

\begin{figure}[tb]
	\centering
	\includegraphics[draft=false]{GrowAndBridge}
	\caption{Merge buildings by introducing bridges when the buildings become 
	too close.
		Although the bridges appear at different time, 
		their widths are the same (see the figure with $t=1$).}
	\label{fig:GrowAndBridge}
\end{figure}

\subsection{Simplify grown buildings}
\label{sec:Simplify}
We use a buffering-based method, 
similar to \textcite{Damen2008,Meijers2016}, 
to simplify our grown buildings. 
We first dilate the grown buildings to remove 
pits, and then erode the results to remove spikes.
At time $t$, we dilate with distance $\dtrm{D}$, 
erode with distance $\dtrm{D}+\dtrm{E}$,
and dilate back with distance $\dtrm{E}$.

@@

\begin{figure}[tb]
	\centering
	\includegraphics[draft=false]{ErosionBreak}
	\caption{.}
	\label{fig:ErosionBreak}
\end{figure}
s

The separation threshold at time $t$ is
\[
d_{\epsilon, t} =t \cdot \epsilon S_\mathrm{g}.s
\]
One may expect that we define 
$d_{\epsilon, t} = \epsilon (S_\mathrm{s}+t(S_\mathrm{g}-S_\mathrm{s}))$
so that $\epsilon= 0.2~\text{mm}$ holds for a map at any scale.
The reason we do not define it as this way is that 
our growth $\dtrm{G}$ (see \eq\ref{eq:d_Gt}) can be arbitrarily small when $t$ 
is small.
In \sect\ref{sec:Simplify}, the erosion operator requires that

>>>>

\begin{figure}[tb]
	\centering
	\includegraphics{GrowAndBridge}
	\caption{Merge buildings by introducing bridges when the buildings become 
	too close.
		Although the bridges appear at different time, 
		their widths are the same (see the figure with $t=1$).}
	\label{fig:GrowAndBridge}
\end{figure}

\subsection{Simplify grown buildings}
\label{sec:Simplify}
We use a buffering-based method, 
similar to \textcite{Damen2008,Meijers2016}, 
to simplify our grown buildings. 
We first dilate the grown buildings to remove 
pits, and then erode the results to remove spikes
(see \fig\ref{fig:RemovePitAndSpike}).
At time $t$, we dilate with distance $\dtrm{D}$, 
erode with distance $\dtrm{D}+\dtrm{E}$,
and dilate back with distance $\dtrm{E}$.

\begin{figure}[tb]
	\centering
	\includegraphics[draft=false]{RemovePitAndSpike}
	\caption{.
	}
	\label{fig:RemovePitAndSpike}
\end{figure}

@@

\begin{figure}[tb]
	\centering
	\includegraphics[draft=false]{ErosionBreak}
	\caption{Dilate the gray polygon, then erode the dilated polygon.
		(a) Dilate and erode with distance $d_1$.
		(b) Dilate and erode with distance $d_2$, where $d_2>d_1$.
		In (a) the result of dilation and erosion is the same as the original 
		polygon, while in (b) the result consists of two parts.
	}
	\label{fig:ErosionBreak}
\end{figure}

The separation threshold at time $t$ is
\[
d_{\epsilon, t} =t \cdot \epsilon S_\mathrm{g}.
\]
One may expect that we define 
$d_{\epsilon, t} = \epsilon (S_\mathrm{s}+t(S_\mathrm{g}-S_\mathrm{s}))$
so that $\epsilon= 0.2~\text{mm}$ holds for a map at any scale.
The reason we do not define it as this way is that 
our growth $\dtrm{G}$ (see \eq\ref{eq:d_Gt}) can be arbitrarily small when $t$ 
is small.
In \sect\ref{sec:Simplify}, the erosion operator requires that
